Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Structure

### 2017-06-19 documents/TriangleScenarioArXiv/ts.tex
Improved compatibility discussion

    \Cref{sec:inflation_technique} briefly summaries the Inflation Technique in the specific context of this work. Although the summary presented here is designed to be self-standing, a much more pedagogical introduction is offered by the original work~\cite{Inflation}. \Cref{sec:deriving_inequalities} demonstrates how the Inflation Technique was used to derive causal compatibility inequalities for the Triangle structure that are violated by quantum-accessible distributions.

@@

    Now that the notion of a causal structure $\graph$ is defined along with some standard graph-theoretic notation, it is now possible to precisely define the notion of compatibility between $\graph$ and a probability distribution $\prob[\nodes]$ defined over the nodes of $\graph$. Intuitively, the absence of certain causal connections within $\graph$ should limit the set of possible observations that can be made on $\graph$. Specifically, the causal structure $\graph$ hypothesizes that if each variable $n \in \nodes$ is causally influenced by its parents $\Pa[\graph]{n}$, then each $n$ should be conditionally independent of all other variables:
    \[ \prob[\nodes] = \prod_{n \in \nodes} \prob[n \mid \Pa[\graph]{n}] = \prob[n_1 \mid \Pa[\graph]{n_1}] \times \cdots \times \prob[n_k \mid \Pa[\graph]{n_k}] \eq \label{eq:compatibility_as_factorization}\]
    % , except its own descendants when conditioned over $\Pa[\graph]{n}$. This is known as the \term{local Markov property}:\footnote{Here $A \indep B \mid C$ denotes statistical independence between $A$ and $B$ conditional on $C$ where $A,B,C \subseteq \nodes$, i.e. for a given probability distribution $\prob[\nodes]$, $\prob[AB \mid C] = \prob[A \mid C]\prob[B \mid C]$.}
    % \[ n \indep \br{\nodes \setminus \De[\graph]{n}} \mid \Pa[\graph]{n} \quad \forall n \in \nodes \eq \label{eq:local_markov_property} \]
    If a given distribution $\prob[\nodes]$ defined over \textit{all} of the nodes $\nodes$ of $\graph$ satisfies \cref{eq:compatibility_as_factorization}, then $\prob[\nodes]$ is said to be \term{compatible with $\graph$}. The conditional distributions in \cref{eq:compatibility_as_factorization} (i.e. $\{\prob[n \mid \Pa[\graph]{n}] \mid n \in \nodes\}$) are referred to as a set of \term{causal parameters for $\graph$}. If a distribution $\prob[\nodes]$ cannot be factorized according to \cref{eq:compatibility_as_factorization}, $\prob[\nodes]$ is said to be \term{incompatible} with $\graph$. The compatibility of a distribution $\prob[\nodes]$ with a causal structure $\graph$ pursuant to \Cref{eq:compatibility_as_factorization} is equivalent to the requirement that $\prob[\nodes]$ obeys all of the conditional independence constraints implied by the \textit{d-separation relations} between variables/nodes in $\graph$~\cite{Pearl_2009}. When one is specified with a joint distribution $\prob[\nodes]$ defined over all nodes of a causal structure $\graph$, it is possible to completely determine whether or not $\prob[\nodes]$ is compatible with $\graph$ by computing the causal parameters induced by $\prob[\nodes]$ and checking the equality of \cref{eq:compatibility_as_factorization}.

@@

    There are several approaches to tackling the compatibility problem when dealing with latent variables; there are two naive approaches worth mentioning here. The first is to recognize that the conditional independence constraints implied by d-separation relations over the \textit{observable} variables form a family of necessary constraints for $\prob[\nodes_{O}]$. The failure to satisfy one of these observable independence relations immediately qualifies $\prob[\nodes_{O}]$ as incompatible with $\graph$. Often, the observable d-separation relations implied by a causal structure form an \textit{insufficient} set of constraints for compatible distributions. Such causal structures, which include the Bell structure, have been termed \textit{interesting}~\cite{Henson_2014}, and more involved classification techniques must be used~\cite{Inflation}. The principle focus of this paper is the Triangle structure and has been shown to be one of the smallest interesting causal structures~\cite{Henson_2014}. An alternative approach requires the cardinality (number of outcomes) of the latent variables to be fixed. In most realistic scenarios, the nature of the latent variables is completely unspecified. More powerful approaches find constraints for $\prob[\nodes]$ in the form of probabilistic inequalities defined over $\prob[\nodes_{O}]$ and its marginals which constraint the set of compatible probability distributions. We term these constraints \term{causal compatibility inequalities}\footnote{We refer to these inequalities as ``causal compatibility inequalities'' instead of Bell inequalities for two reasons. Firstly, ``Bell inequalities'' usually are associated specifically with the Bell structure. Secondly, the inequalities derived in this work are fundamentally distinct from a typical Bell inequality in that these inequalities are \textit{polynomial} over $\prob[\nodes_{O}]$ instead of \textit{linear}.} If a probability distribution $\prob[\nodes_{O}]$ happens to \textit{violate} any causal compatibility inequality, then that distribution deemed \textit{incompatible}. In \cref{sec:deriving_inequalities}, a brief discussion of existing techniques for deriving these inequalities will take place.

@@

    Finally, \citet{Inflation} proposed the Inflation Technique (summarized in \cref{sec:inflation_technique}) --- a novel tool for solving causal inference problems. Using the Inflation Technique, they were able to prove incompatibility between the Triangle structure and the $W$-type distribution; a quantum-inaccessible distribution whose incompatibility is not witness-able by \textit{any} entropic inequalities or any other known constraints. Consequently, as a an algorithmic framework, the Inflation Technique comes closer to characterizing non-classicality in the Triangle structure than all others.

@@

    \Cref{sec:causal_compatibility} defined causal compatibility inequalities while \cref{sec:fritz_distribution} recalled and discussed the Fritz distribution together with a brief summary of its incompatibility with the Triangle structure. Heretofore, there were no known causal compatibility inequalities for the Triangle structure that were capable of witnessing the non-classicality of any quantum distributions~\cite{Inflation}. By leveraging the incompatibility of the Fritz distribution~\cite{Fritz_2012} and tools provided by the Inflation Technique~\cite{Inflation}, we have obtained numerous causal compatibility inequalities for the Triangle structure that are violated by the Fritz distribution. A representative sample of these inequalities are presented here. The methods used to derive these inequalities are largely based on the Inflation Technique~\cite{Inflation}. A summary of the Inflation Technique and other methods used will be deferred to \cref{sec:inflation_technique} where unfamiliar readers will find a succinct yet sufficient presentation of the requisites.

    The first causal compatibility inequality chosen for presentation is reported below:
    \begin{equation*}
    \begin{gathered}
    \eq\label{eq:ww_ineq}
    I\tsb{WagonWheel} : \\
    + P_{ABC}(000)P_{C}(3) - 2P_{ABC}(203)P_{C}(0) - 2P_{ABC}(303)P_{C}(0) - P_{ABC}(003)P_{C}(0) \\
    - P_{ABC}(013)P_{C}(0) - P_{ABC}(020)P_{C}(2) - P_{ABC}(022)P_{C}(2) - P_{ABC}(023)P_{C}(0) \\
    - P_{ABC}(023)P_{C}(2) - P_{ABC}(030)P_{C}(2) - P_{ABC}(031)P_{C}(2) - P_{ABC}(032)P_{C}(2) \\
    - P_{ABC}(033)P_{C}(0) - P_{ABC}(033)P_{C}(2) - P_{ABC}(103)P_{C}(0) - P_{ABC}(113)P_{C}(0) \\
    - P_{ABC}(123)P_{C}(0) - P_{ABC}(133)P_{C}(0) - P_{ABC}(200)P_{C}(0) - P_{ABC}(200)P_{C}(1) \\
    - P_{ABC}(200)P_{C}(2) - P_{ABC}(200)P_{C}(3) - P_{ABC}(201)P_{C}(0) - P_{ABC}(201)P_{C}(1) \\
    - P_{ABC}(201)P_{C}(2) - P_{ABC}(201)P_{C}(3) - P_{ABC}(203)P_{C}(1) - P_{ABC}(203)P_{C}(2) \\
    - P_{ABC}(203)P_{C}(3) - P_{ABC}(213)P_{C}(0) - P_{ABC}(223)P_{C}(0) - P_{ABC}(300)P_{C}(0) \\
    - P_{ABC}(300)P_{C}(1) - P_{ABC}(300)P_{C}(2) - P_{ABC}(300)P_{C}(3) - P_{ABC}(301)P_{C}(0) \\
    - P_{ABC}(301)P_{C}(1) - P_{ABC}(301)P_{C}(2) - P_{ABC}(301)P_{C}(3) - P_{ABC}(302)P_{C}(1) \\
    - P_{ABC}(303)P_{C}(1) - P_{ABC}(303)P_{C}(2) - P_{ABC}(303)P_{C}(3) - P_{ABC}(313)P_{C}(0) \leq 0
    \end{gathered}
    \end{equation*}
    \Cref{eq:ww_ineq} is termed the Wagon Wheel inequality and denoted $I\tsb{WagonWheel}$ after the identically named inflation (\cref{fig:wagon_wheel_inflation}) utilized to derive it. To reiterate, a summary of the methods used to derive \cref{eq:ww_ineq} can be found in \cref{sec:marginal_satisfiability,sec:inflation_technique_main_summary,sec:deriving_inequalities_from_the_inflation_technique}.

@@

    In \cref{sec:found_inequalities}, we presented the first examples of causal compatibility inequalities capable of having quantum violations in the sense that they are violated by quantum-accessible distributions. This result was made possible through extensive use of the Inflation Technique (\cref{sec:inflation_technique}) applied to the Fritz distribution. In the context of Fritz's Problem, our result corresponds to a resolution to the following \textit{reinterpretation} of Fritz's original Problem:
    \begin{enumerate}[label=\textbf{FP.\Alph*}]
        \setcounter{enumi}{0}
        \item \label{r:1} Find proofs for causal incompatibility of quantum distributions on the Triangle structure that are \textit{not} reliant on perfect correlations.
    \end{enumerate}

@@

    The question, as proposed by \ref{r:2}, is: does there exist incompatible quantum distributions that genuinely require the entanglement resources of three states? At first, one might suspect that finding such distributions would affirmatively demonstrate a new form of entanglement resource distinct to the Triangle structure. Unfortunately, this is not the case. By increasing the cardinality of the outcomes for $A, B, C$, it is possible to generate a distribution that is non-classical yet quantum and requires all three of the shared resources to be entangled. This can be accomplished by superimposing three copies of statistically independent Fritz distributions to the Triangle structure, each of which utilizes a distinct party to announce the corresponding measurement pseudo-settings. Such a distribution would be of the form described by \ref{r:2} because under this construction, the removal of any entangled resource would render the distribution quantum-inaccessible. Consequently, it becomes desirable to find non-classical quantum correlations for the Triangle structure which have the fewest number of outcomes. In pursuit of this objective, the authors were able to prove the non-classicality (using the methods described in \cref{sec:inflation_technique}) of a variant of the Fritz distribution where $C$ has only two outcomes: the first corresponding to $A, B$ correlations and the second corresponding to $A, B$ anti-correlations. These advancements suggest the cardinality of measurement outcomes are intimately connected to quantum non-classicality and is a recommended focus for future research.

@@

    \section{Summary of Inflation Technique}
    \label{sec:inflation_technique}

@@

    This section aims to explain how to solve the following decision problem: given a collection of probability distributions $\bc{\prob[V_1], \ldots, \prob[V_m]}$ where each set of variables $V_{i} \subseteq \jointvar$ is a subset of some complete set of variables $\jointvar$, does there exist a joint distribution $\prob[\jointvar]$ such that each $\prob[V_i]$ can be obtained by marginalizing $\prob[\jointvar]$ over the variables not in $V_i$, i.e. $\prob[V_i] = \sum_{\jointvar \setminus V_i} \prob[\jointvar]$? Colloquially, this problem is referred to as \term{the marginal problem}~\cite{Fritz_2011}. Additionally, this section aims to accomplish something further. If such as joint distribution $\prob[\jointvar]$ exists, how does one find it? Moreover, if a joint distribution does not exist, find an inequality that $\bc{\prob[V_1], \ldots, \prob[V_m]}$ fails which proves such a joint distribution does not exist. This is accomplished by illustrating how the marginal problem can be expressed as a linear program in which the solution to the marginal problem is encoded in the feasibility or infeasibility of said linear program. This section is presented prior to \cref{sec:inflation_technique_main_summary} as the marginal problem becomes an integral component of the Inflation Technique in subsequently deriving the inequalities presented in \cref{sec:found_inequalities}. Moreover, the Marginal problem is presented here logically independent from the remainder of the manuscript both for procedural clarity and because the marginal problem has applications to numerous areas of mathematics including game theory~\cite{Vorobev_1962}, database theory, knowledge integration of expert system, and of course, quantum information theory~\cite{Fritz_2011}.

@@

    Each of the above mentioned techniques suffers from computational complexity limitations. For example, the Fourier-Motzkin procedure is in the worst case doubly exponential in the number of initial inequalities~\cite{Dantzig_1973}. For the purposes of this research, solving the marginal problem without reference to a marginal model was intractable. This will become apparent in \cref{sec:deriving_inequalities_from_the_inflation_technique} when the Inflation Technique is applied to the Triangle structure, producing considerably large marginal models. Luckily, the Fritz distribution (\cref{sec:fritz_distribution}) allows one to avoid the complexity issues of the complete marginal problem and instead focus on the original problem of determining whether or not a particular marginal model admits a joint distribution or not.
    \subsection{Inflation Technique}
    \label{sec:deriving_inequalities}
    \label{sec:inflation_technique_main_summary}
    The \term{Inflation Technique}, invented by \citet{Inflation} and inspired by the \textit{do calculus} and \textit{twin networks} of \citet{Pearl_2009}, is a family of causal inference techniques that can be used to determine if an observable probability distribution $\prob[\nodes_{O}]$ is compatible or incompatible with a given causal structure $\graph$. As a precursor, the Inflation Technique begins by \textit{augmenting} a causal structure $\graph$ with additional copies of its nodes, producing an \textit{inflated} causal structure $\graph'$ called an \term{inflation}, and then exposes how causal inference tasks on the inflation can be used to make inferences on the original causal structure. For reference, a few inflations of the Triangle structure are depicted in \cref{fig:inflations}. Copies of nodes in the inflated causal structure are distinguished by an additional subscript called the \term{copy-index}. For example, node $A$ of \cref{fig:triangle_structure} has copies $A_1, A_2, A_3, A_4$ in the inflated causal structure in \cref{fig:the_web_inflation}. All such copies are deemed equivalent via a \term{copy-index equivalence} relation denoted `$\sim$'. A copy-index is effectively arbitrary, so we will refer to an arbitrary inflated copy of $A$ as $A'$, i.e. $A \sim A_1 \sim A' \not\sim B \sim B_1 \sim B'$.\footnote{Note that we preemptively generalize the notion of copy-index equivalence to other mathematical objects like sets, graphs, and groups by saying that $X \sim Y$ if and only if $X$ is equivalent to $Y$ upon removal of the copy-index.}

@@

    \Cref{sec:inflation_technique_main_summary} summarizes how the Inflation Technique~\cite{Inflation} can cast the compatibility problem into the marginal problem by leveraging inflations of the Triangle structure. Explicitly, for a given inflation $\graph'$ of the Triangle structure, one constructs a marginal problem (see \cref{sec:marginal_satisfiability}) for the marginal scenario $\mscenario$ composed of the maximal as-expressible sets of $\graph'$, i.e. $\mscenario = \AnSepExpr[\graph]{\graph'}$.

@@

    \Cref{sec:inflation_technique_main_summary} detailed how to obtain causal compatibility inequalities for any causal structure by constructing a marginal problem (see \cref{sec:marginal_satisfiability}) and supplying an incompatible distribution to generate an infeasibility certificate. In \cref{sec:found_inequalities}, a causal compatibility inequality symmetric under permutations of the variables $A,B,C$ was presented (see \cref{eq:symmetic_web_inequality}). This section aims to describe a general technique that can be used to derive inequalities exhibiting this symmetry. In brief, this is accomplished by grouping marginal events $m \in \Events{\mscenario}$ of a marginal scenario $\mscenario$ into orbits under the action of variable permutations.

>>>>

    \Cref{sec:main_appendix} briefly summaries the Inflation Technique in the specific context of this work. Although the summary presented here is designed to be self-standing, a much more pedagogical introduction is offered by the original work~\cite{Inflation}. \Cref{sec:deriving_inequalities} demonstrates how the Inflation Technique was used to derive causal compatibility inequalities for the Triangle structure that are violated by quantum-accessible distributions.

@@

    Now that the notion of a causal structure $\graph$ is defined along with some standard graph-theoretic notation, it is now possible to precisely define the notion of compatibility between $\graph$ and a probability distribution $\prob[\nodes]$ defined over the nodes of $\graph$. Intuitively, the absence of certain causal connections within $\graph$ should limit the set of possible observations that can be made on $\graph$. Specifically, the causal structure $\graph$ hypothesizes that if each variable $n \in \nodes$ is causally influenced by its parents $\Pa[\graph]{n}$. Therefore, if each variable is conditioned on its parentage, the probability distribution $\prob[\nodes]$ should factorize accordingly:
    \[ \prob[\nodes] = \prod_{n \in \nodes} \prob[n \mid \Pa[\graph]{n}] = \prob[n_1 \mid \Pa[\graph]{n_1}] \times \cdots \times \prob[n_k \mid \Pa[\graph]{n_k}] \eq \label{eq:compatibility_as_factorization}\]
    % , except its own descendants when conditioned over $\Pa[\graph]{n}$. This is known as the \term{local Markov property}:\footnote{Here $A \indep B \mid C$ denotes statistical independence between $A$ and $B$ conditional on $C$ where $A,B,C \subseteq \nodes$, i.e. for a given probability distribution $\prob[\nodes]$, $\prob[AB \mid C] = \prob[A \mid C]\prob[B \mid C]$.}
    % \[ n \indep \br{\nodes \setminus \De[\graph]{n}} \mid \Pa[\graph]{n} \quad \forall n \in \nodes \eq \label{eq:local_markov_property} \]
    If a given distribution $\prob[\nodes]$ defined over \textit{all} of the nodes $\nodes$ of $\graph$ satisfies \cref{eq:compatibility_as_factorization}, then $\prob[\nodes]$ is said to be \term{compatible with $\graph$}. The conditional distributions in \cref{eq:compatibility_as_factorization} (i.e. $\{\prob[n \mid \Pa[\graph]{n}] \mid n \in \nodes\}$) are referred to as a set of \term{causal parameters for $\graph$}. If a distribution $\prob[\nodes]$ cannot be factorized according to \cref{eq:compatibility_as_factorization}, $\prob[\nodes]$ is said to be \term{incompatible} with $\graph$. The compatibility of a distribution $\prob[\nodes]$ with a causal structure $\graph$ pursuant to \Cref{eq:compatibility_as_factorization} is equivalent to the requirement that $\prob[\nodes]$ obeys all of the conditional independence constraints implied by the \textit{d-separation relations} between variables/nodes in $\graph$~\cite{Pearl_2009}. When one is specified with a joint distribution $\prob[\nodes]$ defined over all nodes of a causal structure $\graph$, it is possible to completely determine whether or not $\prob[\nodes]$ is compatible with $\graph$ by computing the causal parameters induced by $\prob[\nodes]$ and checking the equality of \cref{eq:compatibility_as_factorization}.

@@

    There are several approaches to tackling the compatibility problem when dealing with latent variables; there are two common approaches worth mentioning here. The first is to recognize that the conditional independence constraints implied by d-separation relations over the \textit{observable} variables form a family of necessary constraints for $\prob[\nodes_{O}]$. The failure to satisfy one of these observable independence relations immediately qualifies $\prob[\nodes_{O}]$ as incompatible with $\graph$. Often, the observable d-separation relations implied by a causal structure form an \textit{insufficient} set of constraints for compatible distributions. Such causal structures, which include the Bell structure, have been termed \textit{interesting}~\cite{Henson_2014}. For interesting causal structures, stronger techniques must be used~\cite{Inflation}. The primary causal structure of this paper is the Triangle structure --- one of the smallest interesting causal structures~\cite{Henson_2014}. An alternative approach requires the cardinality (number of outcomes) of the latent variables to be fixed. In most realistic scenarios, the nature of the latent variables is completely unspecified. More powerful approaches find constraints for $\prob[\nodes]$ in the form of probabilistic inequalities defined over $\prob[\nodes_{O}]$ and its marginals which constraint the set of compatible probability distributions. We term these constraints \term{causal compatibility inequalities}\footnote{We refer to these inequalities as ``causal compatibility inequalities'' instead of Bell inequalities for two reasons. Firstly, ``Bell inequalities'' usually are associated specifically with the Bell structure. Secondly, the inequalities derived in this work are fundamentally distinct from a typical Bell inequality in that these inequalities are \textit{polynomial} over $\prob[\nodes_{O}]$ instead of \textit{linear}.}. If a probability distribution $\prob[\nodes_{O}]$ happens to \textit{violate} any causal compatibility inequality, then that distribution deemed \textit{incompatible}. \Cref{sec:main_appendix} provides a brief discussion of existing techniques used to derive these inequalities.

@@

    Finally, \citet{Inflation} proposed the Inflation Technique (summarized in \cref{sec:main_appendix}) --- a novel tool for solving causal inference problems. Using the Inflation Technique, they were able to prove incompatibility between the Triangle structure and the $W$-type distribution; a quantum-inaccessible distribution whose incompatibility is not witness-able by \textit{any} entropic inequalities or any other known constraints. Consequently, as a an algorithmic framework, the Inflation Technique comes closer to characterizing non-classicality in the Triangle structure than all others.

@@

    \Cref{sec:causal_compatibility} defined causal compatibility inequalities while \cref{sec:fritz_distribution} recalled and discussed the Fritz distribution together with a brief summary of its incompatibility with the Triangle structure. Heretofore, there were no known causal compatibility inequalities for the Triangle structure that were capable of witnessing the non-classicality of any quantum distributions~\cite{Inflation}. By leveraging the incompatibility of the Fritz distribution~\cite{Fritz_2012} and tools provided by the Inflation Technique~\cite{Inflation}, we have obtained numerous causal compatibility inequalities for the Triangle structure that are violated by the Fritz distribution. A representative sample of these inequalities are presented here. The methods used to derive these inequalities are largely based on the Inflation Technique~\cite{Inflation}. A summary of the Inflation Technique and other methods used will be deferred to \cref{sec:main_appendix} where unfamiliar readers will find a succinct yet sufficient presentation of the requisites.

    The first causal compatibility inequality chosen for presentation is reported below:
    \begin{equation*}
    \begin{gathered}
    \eq\label{eq:ww_ineq}
    I\tsb{WagonWheel} : \\
    + P_{ABC}(000)P_{C}(3) - 2P_{ABC}(203)P_{C}(0) - 2P_{ABC}(303)P_{C}(0) - P_{ABC}(003)P_{C}(0) \\
    - P_{ABC}(013)P_{C}(0) - P_{ABC}(020)P_{C}(2) - P_{ABC}(022)P_{C}(2) - P_{ABC}(023)P_{C}(0) \\
    - P_{ABC}(023)P_{C}(2) - P_{ABC}(030)P_{C}(2) - P_{ABC}(031)P_{C}(2) - P_{ABC}(032)P_{C}(2) \\
    - P_{ABC}(033)P_{C}(0) - P_{ABC}(033)P_{C}(2) - P_{ABC}(103)P_{C}(0) - P_{ABC}(113)P_{C}(0) \\
    - P_{ABC}(123)P_{C}(0) - P_{ABC}(133)P_{C}(0) - P_{ABC}(200)P_{C}(0) - P_{ABC}(200)P_{C}(1) \\
    - P_{ABC}(200)P_{C}(2) - P_{ABC}(200)P_{C}(3) - P_{ABC}(201)P_{C}(0) - P_{ABC}(201)P_{C}(1) \\
    - P_{ABC}(201)P_{C}(2) - P_{ABC}(201)P_{C}(3) - P_{ABC}(203)P_{C}(1) - P_{ABC}(203)P_{C}(2) \\
    - P_{ABC}(203)P_{C}(3) - P_{ABC}(213)P_{C}(0) - P_{ABC}(223)P_{C}(0) - P_{ABC}(300)P_{C}(0) \\
    - P_{ABC}(300)P_{C}(1) - P_{ABC}(300)P_{C}(2) - P_{ABC}(300)P_{C}(3) - P_{ABC}(301)P_{C}(0) \\
    - P_{ABC}(301)P_{C}(1) - P_{ABC}(301)P_{C}(2) - P_{ABC}(301)P_{C}(3) - P_{ABC}(302)P_{C}(1) \\
    - P_{ABC}(303)P_{C}(1) - P_{ABC}(303)P_{C}(2) - P_{ABC}(303)P_{C}(3) - P_{ABC}(313)P_{C}(0) \leq 0
    \end{gathered}
    \end{equation*}
    \Cref{eq:ww_ineq} is termed the Wagon Wheel inequality and denoted $I\tsb{WagonWheel}$ after the identically named inflation (\cref{fig:wagon_wheel_inflation}) utilized to derive it. To reiterate, a summary of the methods used to derive \cref{eq:ww_ineq} can be found in \cref{sec:marginal_satisfiability,sec:main_appendix_main_summary,sec:deriving_inequalities_from_the_inflation_technique}.

@@

    In \cref{sec:found_inequalities}, we presented the first examples of causal compatibility inequalities capable of having quantum violations in the sense that they are violated by quantum-accessible distributions. This result was made possible through extensive use of the Inflation Technique (\cref{sec:main_appendix}) applied to the Fritz distribution. In the context of Fritz's Problem, our result corresponds to a resolution to the following \textit{reinterpretation} of Fritz's original Problem:
    \begin{enumerate}[label=\textbf{FP.\Alph*}]
        \setcounter{enumi}{0}
        \item \label{r:1} Find proofs for causal incompatibility of quantum distributions on the Triangle structure that are \textit{not} reliant on perfect correlations.
    \end{enumerate}

@@

    The question, as proposed by \ref{r:2}, is: does there exist incompatible quantum distributions that genuinely require the entanglement resources of three states? At first, one might suspect that finding such distributions would affirmatively demonstrate a new form of entanglement resource distinct to the Triangle structure. Unfortunately, this is not the case. By increasing the cardinality of the outcomes for $A, B, C$, it is possible to generate a distribution that is non-classical yet quantum and requires all three of the shared resources to be entangled. This can be accomplished by superimposing three copies of statistically independent Fritz distributions to the Triangle structure, each of which utilizes a distinct party to announce the corresponding measurement pseudo-settings. Such a distribution would be of the form described by \ref{r:2} because under this construction, the removal of any entangled resource would render the distribution quantum-inaccessible. Consequently, it becomes desirable to find non-classical quantum correlations for the Triangle structure which have the fewest number of outcomes. In pursuit of this objective, the authors were able to prove the non-classicality (using the methods described in \cref{sec:main_appendix}) of a variant of the Fritz distribution where $C$ has only two outcomes: the first corresponding to $A, B$ correlations and the second corresponding to $A, B$ anti-correlations. These advancements suggest the cardinality of measurement outcomes are intimately connected to quantum non-classicality and is a recommended focus for future research.

@@

    \section{Summary of Inflation Technique}
    \label{sec:main_appendix}

@@

    This section aims to explain how to solve the following decision problem: given a collection of probability distributions $\bc{\prob[V_1], \ldots, \prob[V_m]}$ where each set of variables $V_{i} \subseteq \jointvar$ is a subset of some complete set of variables $\jointvar$, does there exist a joint distribution $\prob[\jointvar]$ such that each $\prob[V_i]$ can be obtained by marginalizing $\prob[\jointvar]$ over the variables not in $V_i$, i.e. $\prob[V_i] = \sum_{\jointvar \setminus V_i} \prob[\jointvar]$? Colloquially, this problem is referred to as \term{the marginal problem}~\cite{Fritz_2011}. Additionally, this section aims to accomplish something further. If such as joint distribution $\prob[\jointvar]$ exists, how does one find it? Moreover, if a joint distribution does not exist, find an inequality that $\bc{\prob[V_1], \ldots, \prob[V_m]}$ fails which proves such a joint distribution does not exist. This is accomplished by illustrating how the marginal problem can be expressed as a linear program in which the solution to the marginal problem is encoded in the feasibility or infeasibility of said linear program. This section is presented prior to \cref{sec:main_appendix_main_summary} as the marginal problem becomes an integral component of the Inflation Technique in subsequently deriving the inequalities presented in \cref{sec:found_inequalities}. Moreover, the Marginal problem is presented here logically independent from the remainder of the manuscript both for procedural clarity and because the marginal problem has applications to numerous areas of mathematics including game theory~\cite{Vorobev_1962}, database theory, knowledge integration of expert system, and of course, quantum information theory~\cite{Fritz_2011}.

@@

    Each of the above mentioned techniques suffers from computational complexity limitations. For example, the Fourier-Motzkin procedure is in the worst case doubly exponential in the number of initial inequalities~\cite{Dantzig_1973}. For the purposes of this research, solving the marginal problem without reference to a marginal model was intractable. This will become apparent in \cref{sec:deriving_inequalities_from_the_inflation_technique} when the Inflation Technique is applied to the Triangle structure, producing considerably large marginal models. Luckily, the Fritz distribution (\cref{sec:fritz_distribution}) allows one to avoid the complexity issues of the complete marginal problem and instead focus on the original problem of determining whether or not a particular marginal model admits a joint distribution or not.
    \subsection{Inflation Technique}
    \label{sec:deriving_inequalities}
    \label{sec:main_appendix_main_summary}
    The \term{Inflation Technique}, invented by \citet{Inflation} and inspired by the \textit{do calculus} and \textit{twin networks} of \citet{Pearl_2009}, is a family of causal inference techniques that can be used to determine if an observable probability distribution $\prob[\nodes_{O}]$ is compatible or incompatible with a given causal structure $\graph$. As a precursor, the Inflation Technique begins by \textit{augmenting} a causal structure $\graph$ with additional copies of its nodes, producing an \textit{inflated} causal structure $\graph'$ called an \term{inflation}, and then exposes how causal inference tasks on the inflation can be used to make inferences on the original causal structure. For reference, a few inflations of the Triangle structure are depicted in \cref{fig:inflations}. Copies of nodes in the inflated causal structure are distinguished by an additional subscript called the \term{copy-index}. For example, node $A$ of \cref{fig:triangle_structure} has copies $A_1, A_2, A_3, A_4$ in the inflated causal structure in \cref{fig:the_web_inflation}. All such copies are deemed equivalent via a \term{copy-index equivalence} relation denoted `$\sim$'. A copy-index is effectively arbitrary, so we will refer to an arbitrary inflated copy of $A$ as $A'$, i.e. $A \sim A_1 \sim A' \not\sim B \sim B_1 \sim B'$.\footnote{Note that we preemptively generalize the notion of copy-index equivalence to other mathematical objects like sets, graphs, and groups by saying that $X \sim Y$ if and only if $X$ is equivalent to $Y$ upon removal of the copy-index.}

@@

    \Cref{sec:main_appendix_main_summary} summarizes how the Inflation Technique~\cite{Inflation} can cast the compatibility problem into the marginal problem by leveraging inflations of the Triangle structure. Explicitly, for a given inflation $\graph'$ of the Triangle structure, one constructs a marginal problem (see \cref{sec:marginal_satisfiability}) for the marginal scenario $\mscenario$ composed of the maximal as-expressible sets of $\graph'$, i.e. $\mscenario = \AnSepExpr[\graph]{\graph'}$.

@@

    \Cref{sec:main_appendix_main_summary} detailed how to obtain causal compatibility inequalities for any causal structure by constructing a marginal problem (see \cref{sec:marginal_satisfiability}) and supplying an incompatible distribution to generate an infeasibility certificate. In \cref{sec:found_inequalities}, a causal compatibility inequality symmetric under permutations of the variables $A,B,C$ was presented (see \cref{eq:symmetic_web_inequality}). This section aims to describe a general technique that can be used to derive inequalities exhibiting this symmetry. In brief, this is accomplished by grouping marginal events $m \in \Events{\mscenario}$ of a marginal scenario $\mscenario$ into orbits under the action of variable permutations.
